---
title: "Graphics with ggplot2"
author: "AEM"
date: "October 22, 2018"
output: html_document
---

# Learning ggplot2

Day 1 Software Carpentry workshop learning ggpot2
```{r}

##instal packages
###install.packages('tidyverse')

##loading package 
###library(tidyverse)



#National Parks in California
ca <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/ca.csv") 

#Acadia National Park
acadia <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/acadia.csv")

#Southeast US National Parks
se <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/se.csv")

#2016 Visitation for all Pacific West National Parks
visit_16 <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/visit_16.csv")

#All Nationally designated sites in Massachusetts
mass <- read_csv("https://raw.githubusercontent.com/OHI-Science/data-science-training/master/data/mass.csv")

```

Data --> park visitation rates

Start with California ('ca') dataset
```{r}
head(ca)
```

## Plotting visitation to all CA national parks over time
```{r}
ggplot(data = ca) +
  geom_point(aes(x = year, y = visitors))
```

## Plotting, adding park name color cord
```{r}
ggplot(data = ca) +
  geom_point(aes(x = year, y = visitors, color = park_name))
```

## Plotting, adding park name color cord
```{r}
ggplot(data = ca) +
  geom_point(aes(x = year, y = visitors, color = park_name)) +
  labs(x = "Year",
       y = "Visitation",
       title = "California National Park Visitation")

```


## plotting se data 

```{r}
#head(se)
ggplot(data = se) +
  geom_point(aes(x = year, y = visitors, color = state)) +
  labs(x = "Year", 
       y = "Visitation",
       title = "Southeast National Park Visitation") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle =45, size = 14))
```

## Faceting plots
```{r}
ggplot(data = se) +
  geom_point(aes(x = year, y = visitors, color = park_name)) +
  facet_wrap(~ state, scales = "free_y") +
  theme(axis.text.x = element_text(angle = 90))
```

# geoms
```{r}
ggplot(data = se) +
  geom_jitter(aes(x = park_name, y = visitors, color = year), alpha = 0.4, width = 0.4) +
  theme(axis.text.x = element_text(angle = 90))
```


## line geom
```{r}
ggplot(se) +
  geom_line(aes(x = year, y = visitors, color = park_name)) +
  theme_bw()
```


## multiple geoms on one plot
```{r}
ggplot(data = acadia) +
  geom_point(aes(x = year, y = visitors))+
  geom_line(aes(x = year, y = visitors))
```
## removing redundancy in aboev code
```{r}
ggplot(data = acadia, aes(x = year, y = visitors)) +
  geom_point() +
  geom_line()
```


#installl more themes
```{r}
#install.packages('ggthemes')
#library(ggthemes)
```

## bar charts
```{r}
ggplot(data = visit_16, aes(x = state, y = visitors, fill = park_name)) +
  geom_bar(stat = "identity") +
  theme_bw()
```

## save a ggplot
```{r}
myplot <- ggplot(data = visit_16, aes(x = state, y = visitors, fill = park_name)) +
  geom_bar(stat = "identity") +
  theme_bw()

ggsave(filename = "myplot.png", myplot)
```

